Program Optimisations via Hylomorphisms for Extraction of Executable Code

### 2025-07-07 paper/paper.tex
Fixed awkward line break

This program is the same as composing a \emph{quicksort} OCaml implementation,
with the function \ocaml{map (fun x -> x * 2)} which is a known program
optimisation called \emph{fusion}.  A lot of program calculations have this
pattern: start from a simple specification, e.g.\
$\mathsf{map}\;(\lambda x.\;x \times 2) \circ \mathsf{sort}$, and use program
equivalences and algebraic laws to rewrite it to an optimised version. We will
revisit a similar example in Section~\ref{sec:sorting}.

>>>>

This program is the same as composing a \emph{quicksort} OCaml implementation,
with the function \ocaml{map (fun x -> x * 2)} which is a known program
optimisation called \emph{fusion}.  A lot of program calculations have this
pattern: start from a simple specification, e.g.
\\$\mathsf{map}\;(\lambda x.\;x \times 2) \circ \mathsf{sort}$, and use program
equivalences and algebraic laws to rewrite it to an optimised version. We will
revisit a similar example in Section~\ref{sec:sorting}.
